Two years of CiTO annotations

### 2022-08-28 article.Rmd
Added the Connected Papers reference, see https://twitter.com/ConnectedPapers/status/1563477087541170176

With the use of citations increasingly being picked up to help researchers with tools like
scite.ai [@citesAsAuthority:Nicholson_2021] en Connected Papers, having typed
citations will help us explore literature. Therefore, the *Journal of Cheminformatics*
started a pilot for the adoption of annotating citations with their annotations [@discusses:Willighagen_2020].

>>>>

With the use of citations increasingly being picked up to help researchers with tools like
scite.ai [@citesAsAuthority:Nicholson_2021] en Connected Papers [@citesAsAuthority:ConnectedPapers], having typed
citations will help us explore literature. Therefore, the *Journal of Cheminformatics*
started a pilot for the adoption of annotating citations with their annotations [@discusses:Willighagen_2020].
